A fast GPU solver for near-Toeplitz tridiagonal systems

### 2015-11-02 paper-draft/paper.tex
move stuff around

\pagebreak
%----------------------------------------------------------------------%
\section{Results: single GPU} \label{sec:results-single-gpu}
%----------------------------------------------------------------------%

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-bench-2d.eps}
\end{center}
\label{fig:k20-bench-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-bench-3d.eps}
\end{center}
\label{fig:k20-bench-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-global-vs-shared-2d.eps}
\end{center}
\label{fig:k20-global-vs-shared-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/k20-global-vs-shared-3d.eps}
\end{center}
\label{fig:k20-global-vs-shared-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=250pt]{fig/k20-forward-vs-backward.eps}
\end{center}
\label{fig:k20-forward-vs-backward}
\end{figure}

>>>>

\pagebreak
%----------------------------------------------------------------------%
\section{Results} \label{sec:results-single-gpu}
%----------------------------------------------------------------------%

\subsection{Global memory v/s shared memory solver performance}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/global-vs-shared-2d.eps}
\end{center}
\label{fig:global-vs-shared-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[height=200pt]{fig/global-vs-shared-3d.eps}
\end{center}
\label{fig:global-vs-shared-3d}
\end{figure}

In Figures \ref{fig:global-vs-shared-2d} and \ref{fig:global-vs-shared-3d},
we report the performance of the two solvers for the case
$N_{rhs} = n$ and $N_{rhs} = n^2$.
These cases correspond to tridiagonal systems
arising in 2-D and 3-D problems respectively.

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/bench-2d.eps}
\end{center}
\label{fig:k20-bench-2d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/bench-3d.eps}
\end{center}
\label{fig:k20-bench-3d}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=250pt]{fig/phases-analysis.eps}
\end{center}
\label{fig:k20-forward-vs-backward}
\end{figure}
